Digital History in Finland, 1488-1828

### 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
ok

```{r 20150912-HDH-Author, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=12}
p1 <- top_plot(dfo, "author", 10) + ggtitle(paste("Top authors (", min(na.omit(dfo$publication_year)), "-", max(na.omit(dfo$publication_year)), ")", sep = ""))

p2 <- top_plot(df, "author", 10) + ggtitle(paste("Top authors (", min(na.omit(df$publication_year)), "-", max(na.omit(df$publication_year)), ")", sep = ""))

>>>>

```{r 20150912-HDH-Author, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=12}
p1 <- top_plot(dfo, "author", 10) + ggtitle(paste("Top authors (", min(na.omit(dfo$publication_year)), "-", max(na.omit(dfo$publication_year)), ")", sep = "")) + ylab("Title count (n)")

p2 <- top_plot(df, "author", 10) + ggtitle(paste("Top authors (", min(na.omit(df$publication_year)), "-", max(na.omit(df$publication_year)), ")", sep = "")) + ylab("Title count (n)")
